\section{\texorpdfstring{\faHistory}{}\ Experience}

\role{Senior Data Scientist}{Unique Computing LLC}{2021}{Present}
Successfully delivered various projects that involved data processing, visualization, model development and performance tuning, API development, and cross-platform application development with deployed models. Some of my responsibilities and achievements are:
\begin{itemize}[parsep=0.5ex]
    \item {build end-to-end machine learning solutions, from data acquisition and processing to model deployment and monitoring with MLOps (CI/CD) tools and frameworks.}
    \item {Help businesses retain customers by predicting possible customer churn using advanced machine learning techniques. This resulted in significant savings for the clients due to reduced customer acquisition costs and increased customer loyalty.}
    \item {Utilize Generative AI to create customer facing solutions that help businesses understand their customers better.}
\end{itemize}
\small{\textbf{Job Skills:}
    AI/ML, Generative AI, NLP, Speech Recognition, Computer Vision, Software Engineering, Cloud Computing (AWS, DataBricks), Application Development, CI/CD tools, Git, API development, Relational Databases, Flutter.
}
\role{Software Engineer}{Freelance}{2017}{2021}
Extensive real world experience in data science, data analysis, project management, applications and web development. Some of the skills and tasks include:
\begin{itemize}[parsep=0.5ex]
    \item {Assist clients in understanding data with data analysis and visualization techniques, such as descriptive statistics, exploratory data analysis, and interactive dashboards.}
          \item{develop and deploy various desktop and web applications that integrated model APIs to provide solutions for different domains and use cases.}
\end{itemize}

\small{\textbf{Job Skills:}
    C, C++, Python, Java, JavaFx, JavaScript, HTML, CSS, Data Structure and Algorithms, Dynamic programming, Machine Learning, Numpy, Pandas, Scikit-Learn, SQL, Figma, Web Development.
}